03_wrangle

### 2020-08-26 analysis/03_datawrangling.Rmd
new female stuff

```{r write}
write.csv(allDEG, "../results/03_allDEG.csv", row.names = F)
write.csv(candidatevsd, "../results/03_candidatevsd.csv")
write.csv(wideDEGsSequential, "../results/table1.csv", row.names = F)

write.csv(removalDEGs, "../results/removalDEGs.csv")
write.csv(hatchDEGs, "../results/hatchDEGs.csv")
write.csv(prolongDEGs, "../results/prolongDEGs.csv")

write.csv(manipDEGs, "../results/manipDEGs.csv")

@@

### overlapp

@@

@@

venn.diagram(
  x = list(hatch_m.n2DEGs, inc.d17_m.inc.d17DEGs, 
           inc.d3_m.inc.d3DEGs, inc.d9_m.inc.d9DEGs),
  category.names = c("Inc 3" , "Hatch" , "Inc 9", " Inc 17"),
  filename = '../figures/venn.png',
  output=FALSE,
  col=c("#CDCDCD", '#262625', '#959595','#959595'),
  fill = c("#CDCDCD", "#262625", "#959595", "#959595"),
  main = "No. of genes that respond to offspring removal",
  sub = "9 shared genes: \nPHGDH, NRG2, LHX9, SSTR3, VTN, SARM1, ALK, LPAR1, and APOH" )

>>>>

```{r write}
#write.csv(allDEG, "../results/03_allDEG.csv", row.names = F)
#write.csv(candidatevsd, "../results/03_candidatevsd.csv")
#write.csv(wideDEGsSequential, "../results/table1.csv", row.names = F)

#write.csv(removalDEGs, "../results/removalDEGs.csv")
#write.csv(hatchDEGs, "../results/hatchDEGs.csv")
#write.csv(prolongDEGs, "../results/prolongDEGs.csv")

#write.csv(manipDEGs, "../results/manipDEGs.csv")

@@

### overlap

@@

filteredDEGs <- allDEG %>%
  filter(lfc > 1.1 | lfc < -1.1 ) %>%
  filter(tissue == "gonad")

@@

venn.diagram(
  x = list(hatch_m.n2DEGs, inc.d17_m.inc.d17DEGs, 
           inc.d3_m.inc.d3DEGs, inc.d9_m.inc.d9DEGs),
  category.names = c("Inc 3" , "Hatch" , "Inc 9", " Inc 17"),
  filename = '../figures/venn-gonad.png',
  output=FALSE,
  print.mode = "raw",
  col=c("#CDCDCD", '#262625', '#959595','#959595'),
  fill = c("#CDCDCD", "#262625", "#959595", "#959595"),
  main = "Gonads",
  sub = "zero genes respond to all four offspring removal manipulations"
  #main = "Pituitary",
  #sub = "Six genes respond to all four offspring removal manipulations\n SSTR3, VTN, SARM1, ALK, LPAR1, and PHGDH"
  #main = "Hypothalamus",
  #sub = "Zero genes respond to all four offspring removal manipulations"
  #main = "No. of genes that respond to offspring removal",
  #sub = "9 shared genes: \nPHGDH, NRG2, LHX9, SSTR3, VTN, SARM1, ALK, LPAR1, and APOH"
  )
